Agda Meets Accelerate

### 2012-11-30 paper/main.tex
source code ref added

@@

Finally, the type translation of Agda's FFI has many shortcomings that
cause a number of problems when transporting information between Agda
and Haskell. One part of the problem is, unfortunately, the rich type
structure of Accelerate's API which already encodes many useful
constraints. An alternative, untyped (or less-typed) interface to
Accelerate would make the adaptation to an Agda frontend simpler.

>>>>

\noindent
Source code is available at \url{https://github.com/mchakravarty/accelerate-agda}.

@@

Finally, the type translation of Agda's FFI has a number of shortcomings that
cause problems when transporting information between Agda
and Haskell. One part of the problem is, unfortunately, the rich type
structure of Accelerate's API which already encodes many useful
constraints. An alternative, untyped (or less-typed) interface to
Accelerate would make the adaptation to an Agda frontend simpler.
